Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-07-03 Scripts/Initial_Analysis.Rmd
re-ran untill 2005

EstPropChange <- function(taxon_key,
                          year,
                          hist_y,
                          data_type = "Catch",
                          ensemble_list, # expects a list of ensembles to averrage by
                          path,
                          neighbours){

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      dbem_import,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
      path = path
    )
  )

@@

  # Save Result
  name <- paste("proportion_",taxon_key,".csv",sep="")
  path_name <- paste(result_path,"Proportion/",name, sep="")

@@

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- my_path("D", extra_path = "Species/", name="Transboundary_spp.csv", read = TRUE) %>% 
  clean_names() %>% 
  select(-x1)

@@

# Year timeframe
year_df <- tibble(year =  c(seq(1951,2000,1), seq(2001,2099,1)),
                  time_period = c(rep("historic", 50), rep("future", 99))
                  )

# Data path
path = DBEM_path

# List of ensemble members
ensemble_list <- seq(102,103,1) # for testing
# ensemble_list <- seq(102,111,1)

>>>>

EstPropChange <- function(taxon_key,
                          year,
                          hist_y = 2005,
                          data_type = "Catch",
                          ensemble_list, # expects a list of ensembles to averrage by
                          path,
                          neighbours){

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      read_dbem_ens,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
       model = "GFDL",
      rcp = 85,
      path = "",
    )
  )

@@

  # Save Result
  name <- paste("proportion_",taxon_key,".csv",sep="")
  path_name <- my_path("R",extra_path = "Proportion")

@@

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- my_path("D", extra_path = "Species/", name="Transboundary_spp.csv", read = TRUE) %>% 
  clean_names() %>% 
  select(-v1)

@@

# Year timeframe
year_df <- tibble(year =  c(seq(1951,2005,1), seq(2006,2099,1)),
                  time_period = c(rep("historic", 55), rep("future", 94))
                  )
